---
title: "About Me"
site: distill::distill_website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    css: site.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(htmltools)

# Get last Git commit date (from push) if available
last_update <- tryCatch({
  sys_out <- system("git log -1 --format=%cd --date=unix", intern = TRUE)
  if (length(sys_out) == 0) "" else as.numeric(sys_out[1])
}, error = function(e) NULL)

if (!is.null(last_update) && last_update != "") {
  last_update_ct <- as.POSIXct(last_update, origin = "1970-01-01", tz = "America/Halifax")
  formatted_date <- format(last_update_ct, "%d %B %Y, %H:%M")
} else {
  formatted_date <- format(Sys.time(), "%d %B %Y, %H:%M", tz = "America/Halifax")
}
```

## Contact & Connect

**Email:** [amrose@hollandcollege.com](mailto:amrose@hollandcollege.com)  
**Phone:** [902-888-6748](tel:+19028886748)  
**Address:** Waterfront Campus, 98 Water Street, Summerside, PE   
**Office:** Room 57 


## Background

I'm originally from [Harbour Grace, Newfoundland](https://www.hrgrace.ca/). My academic journey spans:

- **BSc (Joint Hons) Applied Math & Physics** — Research in numerical methods for adaptive mesh generation under Dr. Ronald Haynes
- **MSc Mathematics** — Theoretical research on black hole geometry under Dr. Hari Kunduri
- **BEd Intermediate/Secondary Education** — Teaching internship at Prince of Wales Collegiate, St. John's

My professional experience includes:
- Post-secondary mathematics instructor at College of the North Atlantic (2019–2021)
- Health Information Specialist at Health PEI (statistical analysis and data visualization)
- Learning Manager of Mathematics and Physics at Holland College (2022–present)

## Service & Community

- Faculty Representative, Holland College Accessibility and Inclusion Advisory Council
- Member, City of Charlottetown Affordable Housing Advisory Board
- Trustee, Public Schools Branch (PEI) — Chair, Finance & Audit Committee

## Personal

In my spare time, I enjoy outdoor activities — from relaxing beach trips to day-long hiking expeditions. Growing up in Newfoundland gave me ample opportunity to explore nature, a passion I continue on beautiful Prince Edward Island. I live in Charlottetown with my wife and our six pets (2 dogs and 4 cats).

```{r}
paths <- c("images/gm1.jpeg","images/gm2.jpeg","images/table1.jpeg","images/pei1.jpeg", "images/pei2.jpeg", "images/Bo1.jpeg")
caps <- c("Trail leading to the base of Gros Morne Mountain, Gros Morne National Park, Newfoundland", "View from the way down Gros Morne Mountain, Gros Morne National Park, Newfoundland", "View from the top of the Tablelands, Gros Morne National Park, Newfoundland", "Scenery between Cape Tryon Lighthouse and New London Lighthouse, Prince Edward Island", "Scenery between Cape Tryon Lighthouse and New London Lighthouse, Prince Edward Island", "One of my dogs enjoying a doggy sundae, Charlottetown, Prince Edward Island")
pixture::pixgallery(paths, caption = caps)
```
```{js}
// Open all external links in a new tab
document.addEventListener('DOMContentLoaded', function() {
  var links = document.getElementsByTagName('a');
  for (var i = 0; i < links.length; i++) {
    if (links[i].hostname !== window.location.hostname && links[i].hostname !== '') {
      links[i].setAttribute('target', '_blank');
      links[i].setAttribute('rel', 'noopener noreferrer');
    }
  }
});
```

```{r echo=FALSE}
htmltools::tags$p(
  paste0(
    "Last updated ",
    format(Sys.time(), "%d %B %Y, %H:%M", tz = "America/Halifax"),
    " (Atlantic)."
  ),
  style = "font-size:0.75rem;color:#6c757d;text-align:center;margin-top:2.5rem;margin-bottom:0;"
)
```