---
title: "About Me"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Contact & Connect

**Email:** [amrose@hollandcollege.com](mailto:amrose@hollandcollege.com)  
**Phone:** [902-888-6748](tel:+19028886748)  
**Office:** Room 57, Waterfront Campus, 98 Water Street, Summerside, PE 


## Background

I'm originally from [Harbour Grace, Newfoundland](https://www.hrgrace.ca/). My academic journey spans:

- **BSc (Joint Hons) Applied Math & Physics** — Research in numerical methods for adaptive mesh generation under Dr. Ronald Haynes
- **MSc Mathematics** — Theoretical research on black hole geometry under Dr. Hari Kunduri
- **BEd Intermediate/Secondary Education** — Teaching internship at Prince of Wales Collegiate, St. John's

My professional experience includes:
- Post-secondary mathematics instructor at College of the North Atlantic (2019–2021)
- Health Information Specialist at Health PEI (statistical analysis and data visualization)
- Learning Manager of Mathematics and Physics at Holland College (2022–present)

## Service & Community

- Faculty Representative, Holland College Accessibility and Inclusion Advisory Council
- Member, City of Charlottetown Affordable Housing Advisory Board
- Trustee, Public Schools Branch (PEI) — Chair, Finance & Audit Committee

## Personal

```{r}
paths <- c("images/gm1.jpeg","images/gm2.jpeg","images/table1.jpeg","images/pei1.jpeg", "images/pei2.jpeg", "images/Bo1.jpeg")
caps <- c("Trail to Gros Morne Mountain base, Gros Morne NP, NL", "View from Gros Morne descent, Gros Morne NP, NL", "View from the Tablelands summit, Gros Morne NP, NL", "Scenery: Cape Tryon to New London Lighthouses, PEI", "Coastal scenery between lighthouses, PEI", "One of my dogs enjoying a doggy sundae, Charlottetown, PEI")
pixture::pixgallery(paths, caption = caps)
```

In my spare time, I enjoy outdoor activities — from relaxing beach trips to day-long hiking expeditions. Growing up in Newfoundland gave me ample opportunity to explore nature, a passion I continue on beautiful Prince Edward Island. I live in Charlottetown with my wife and our six pets (2 dogs and 4 cats).

```{r echo=FALSE}
htmltools::tags$p(
  paste0(
    "Last updated ",
    format(Sys.time(), "%d %B %Y, %H:%M", tz = "America/Halifax"),
    " (Atlantic)."
  ),
  style = "font-size:0.75rem;color:#6c757d;text-align:center;margin-top:2.5rem;margin-bottom:0;"
)
```