---
title: "Academic Publications"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Theses

### MSc (Mathematics)

**Title:** Constructing Static Black Hole–Soliton Spacetimes

**Supervisor:** Dr. Hari Kunduri

**Institution:** Memorial University of Newfoundland

**Year:** 2019

**Abstract:** This thesis explores the construction of static black hole–soliton spacetimes in general relativity. We investigate solutions to Einstein's field equations that combine both black hole and soliton components, examining their geometric properties and physical significance in higher-dimensional theories of gravity.

---

## Other Academic Work

- [RPubs collection](https://rpubs.com/andrewmrose/) — notebooks, data analysis, and research experiments

---

## Research Interests

- General relativity and black hole spacetimes
- Soliton solutions in field theory
- Mathematical physics
- Data analysis and scientific computing

```{r echo=FALSE}
htmltools::tags$p(
  paste0(
    "Last updated ",
    format(Sys.time(), "%d %B %Y, %H:%M", tz = "America/Halifax"),
    " (Atlantic)."
  ),
  style = "font-size:0.75rem;color:#6c757d;text-align:center;margin-top:2.5rem;margin-bottom:0;"
)
```