---
title: "Resources"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Links are grouped for quicker scanning. All open in the same tab unless your browser is configured otherwise.

## Community

### Housing & Shelter
[PEI Fight for Affordable Housing](https://peifah.ca/)  
[Anderson House](https://www.fvps.ca/anderson-house/)  
[Chief Mary Bernard Memorial Women's Shelter](https://cmbmws.ca/get-help/)  
[Blooming House](https://bloominghouse.ca/)  
[Deacon House](https://pei.bridgethegapp.ca/adult/service-directory/deacon-house/)  
[Emergency Housing Services](https://pei.bridgethegapp.ca/service-directory/service_directory_tag/housing-emergency-shelter/)  

### Food Assistance
[PEI Food Exchange](https://www.foodexchangepei.com/)  
[PEI Community Fridge](https://linktr.ee/peicommunityfridge)  
[Meals on Wheels PEI](https://vrcpei.org/meals-on-wheels/)  
[Upper Room Hospitality Ministry](https://www.urhm.org/)  

### Health & Mental Health
[Mental Health Services](https://www.princeedwardisland.ca/en/information/health-pei/mental-health-services)  
[PEI Rape and Sexual Assault Centre](https://www.peirsac.org/what-we-do)  
[PEI Family Violence Prevention Services](https://www.fvps.ca/)  
[PEI Crisis Line](https://www.peiers.ca/) *(1‑800‑218‑2885)*  

### LGBTQ+ & Identity
[Pride PEI](https://www.pridepei.ca/)  
[PEI Transgender Network](https://www.peitn.com/home)  
[PEERS Alliance](https://www.peersalliance.ca/)  

### Indigenous & Immigrant Services
[Native Council of PEI](https://ncpei.com/)  
[Immigrant & Refugee Services Association PEI](https://www.irsapei.ca/en/home)  
[BIPOC USHR PEI](https://www.bipocushr.org/)  

### Legal & Human Rights
[PEI Human Rights Commission](https://www.peihumanrights.ca/)  

### Transportation
[Transit PEI](https://transitpei.ca/)  
[T3 Transit](https://www.t3transit.ca/)  

### Libraries & Municipal
[City of Charlottetown](https://www.charlottetown.ca/)  
[City of Summerside](https://www.summerside.ca/)  
[Charlottetown Library](https://www.princeedwardisland.ca/en/point-interest/charlottetown-library-learning-centre-0)  
[Summerside Library](https://www.princeedwardisland.ca/en/point-interest/summerside-rotary-library)  
[PEI Public Libraries (main portal)](https://www.princeedwardisland.ca/en/topic/public-libraries)  

### General Help
[211 PEI](https://pei.211.ca/) – central helpline for social services  

## Academic and career

### Holland College
[Academic Support - Holland College](https://www.hollandcollege.com/admissions/academic-support.html)  
[Office of Retention, Part-Time Study & Career Services - Holland College](https://www.hollandcollege.com/campus-life/office-of-retention-part-time-study-and-career-services.html)  
[Residence Services - Holland College](https://www.hollandcollege.com/campus-life/living-in-residence.html)  
[Off Campus Housing - Holland College](https://www.hollandcollege.com/campus-life/living-off-campus.html)  
[Academic Calendar - Holland College](https://www.hollandcollege.com/admissions/2022-2023-calendar.html)  
[Library Services - Holland College](https://hollandcollege.libguides.com/c.php?g=715197)  
[Money Matters - Holland College](https://www.hollandcollege.com/admissions/money-matters/)  
[Financial Aid - Holland College](https://www.hollandcollege.com/admissions/money-matters/financial-aid.html)  
[Student Jobs - Holland College](https://www.hollandcollege.com/jobs.html)  
[Health Clinics - Holland College](https://www.hollandcollege.com/campus-life/health-clinics.html)  
[Health Services - Holland College](https://www.hollandcollege.com/campus-life/health-services.html)  
[Counselling Services - Holland College](https://www.hollandcollege.com/campus-life/counselling-services.html)  

### Free textbooks & online learning
[OpenStax](https://openstax.org/)  
[American Institute of Mathematics - Open Textbook Initiative](https://aimath.org/textbooks/approved-textbooks/)  
[LibreText - Math](https://math.libretexts.org/Bookshelves)  
[LibreText - Stats](https://stats.libretexts.org/Bookshelves)  
[LibreText - Physics](https://phys.libretexts.org/Bookshelves)  
[BCcampus OpenEd](https://open.bccampus.ca/)  
[MIT OpenCourseWare](https://ocw.mit.edu/)  
[Khan Academy](https://www.khanacademy.org/)  

### Career & job search
[Job Bank PEI](https://www.jobbank.gc.ca/home)  
[WorkPEI](https://www.workpei.ca/)  
[Indeed PEI](https://ca.indeed.com/l-Charlottetown,-PE-jobs)  

### Study skills
[Purdue OWL](https://owl.purdue.edu/)  
[Zotero](https://www.zotero.org/)  

```{js, echo=FALSE}
// Open all external links in a new tab
document.addEventListener('DOMContentLoaded', function() {
  var links = document.getElementsByTagName('a');
  for (var i = 0; i < links.length; i++) {
    if (links[i].hostname !== window.location.hostname) {
      links[i].setAttribute('target', '_blank');
      links[i].setAttribute('rel', 'noopener noreferrer');
    }
  }
});

```{r echo=FALSE}
htmltools::tags$p(
  paste0(
    "Last updated ",
    format(Sys.time(), "%d %B %Y, %H:%M", tz = "America/Halifax"),
    " (Atlantic)."
  ),
  style = "font-size:0.75rem;color:#6c757d;text-align:center;margin-top:2.5rem;margin-bottom:0;"
)
```